An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-05 ex3/paper/paper.tex
Few paper changes

Then we investigate the question whether adversarial samples can be found for this type of data. This is not a trivially answerable question since adversarial samples have mostly been analyzed in the context of computer vision. Our scenario significantly deviates from this in several ways because \begin{enumerate*}
\item the number of features is significantly smaller and
\item only certain features can be manipulated (for example the destination port cannot be manipulated)
\end{enumerate*}.

Surprisingly, we can confirm that adversarial samples can be found even when considering the tight constraints mentioned before. Thus we argue that traditional methods like accuracy are not sufficient for evaluating security-sensitive \gls{ml} systems. The new performance score \gls{ars} precisely captures the notion of how easily an adversary can generate adversarial samples.

Astonishingly, feature importance method reveal that the manipulable features, that are left for adversaries to modify are not even particularly significant for the classification outcome. %Especially the first packets of a flow are critical for determining the decision of a recurrent \gls{ids}.

@@

\autoref{tab:performance_results} shows that our classifier achieves an accuracy that is similar previous work based on these datasets~\cite{meghdouri_analysis_2018}. However unlike these classifiers, our recurrent classifier has the advantage that it can detect attacks already before they are over.

>>>>

With the recent rise of interest in \gls{aml} techniques, also \gls{aml} for \glspl{ids} have been investigated. E.g. \cite{Bachl2019} investigates remedies for poisoning attacks on \glspl{ids}.
In this research, we investigate whether adversarial samples can be found for \gls{ml} based on \glspl{rnn}. This is not a trivially answerable question since adversarial samples have mostly been analyzed in the context of computer vision. Our scenario significantly deviates from this in several ways because \begin{enumerate*}
\item the number of features is significantly smaller and
\item only certain features can be manipulated by an adversary (for example the destination port cannot be manipulated)
\end{enumerate*}.

Surprisingly, we can confirm that adversarial samples can be found even when considering thse tight constraints. % mentioned before.
Thus, we argue that traditional methods like accuracy are not sufficient for evaluating security-sensitive \gls{ml} systems.
We propose the \acrfull{ars} as a new performance score, which precisely captures the notion of how easily an adversary can generate adversarial samples.

Astonishingly, feature importance methods reveal that the manipulable features, that are left for adversaries to modify are not even particularly significant for the classification outcome. %Especially the first packets of a flow are critical for determining the decision of a recurrent \gls{ids}.

@@

\autoref{tab:performance_results} shows that our classifier achieves an accuracy that is similar previous work based on these datasets~\cite{meghdouri_analysis_2018,Bachl2019}. However unlike these classifiers, our recurrent classifier has the advantage that it can detect attacks already before they are over.
